---
title: "FA2" 
author: "SEC1-APM1110_Group14-Awit, Julia Theressa, Deloyola, Jhen Reyniel-FA2" 
output: pdf_document
date: "02-09-2025"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
```
#Github Link: https://github.com/xoxoreyniel/APM1110/blob/main/SEC1-APM1110_Group14-Awit%2C%20Julia%20Theressa%2C%20Deloyola%2C%20Jhen%20Reyniel-FA2.rmd 

2. An experiment consists of tossing two fair coins. Use R to simulate this experiment 100 times and obtain the relative frequency of each possible outcome. Hence, estimate the probability of getting one head and one tail in any order. 
```{r}
set.seed(123)

coin1 <- sample(c("head", "tail"), size=100, replace=TRUE, prob = c(0.5, 0.5))
coin2 <- sample(c("head", "tail"), size=100, replace=TRUE, prob = c(0.5, 0.5))
result <- paste(coin1, coin2, sep="-") 
freq <- table(result)
print("Relative Frequency: ")
print(freq)
prob <- sum(freq[c("head-tail", "tail-head")])
print("Estimate the probability of getting one head and one tail in any order: ")
```

3. An experiment consists of rolling a die. Use R to simulate this experiment 600 times and obtain the relative frequency of each possible outcome. Hence, estimate the probability of getting each of 1, 2, 3, 4, 5, and 6.

```{r}
set.seed(123)

rolls <- sample(1:6, size=600, replace=TRUE)
freq <- table(rolls)/600
prob <- freq 
print("Relative Frequencies:") 
print(freq)
print("Estimated Probabilites:") 
print(prob)
```


