---
title: "FA4" 
author: "SEC1-APM1110_Deloyola, Jhen Reyniel-FA4" 
output: pdf_document
date: "03-03-2025"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
``` 
#Github Link: 

6.1.5 A geospatial analysis system has four sensors supplying images. The percentage of images supplied by each sensor and the percentage of images relevant to a query are shown in the following table. 

What is the overall percentage of relevant images?  
```{r}
sensors <- data.frame(
  sensor = 1:4,
  supplied = c(15, 20, 25, 40),
  relevant = c(50, 60, 80, 85)
)

# Calculate the overall relevant percentage
overall_percentage <- sum(sensors$supplied * sensors$relevant) / 100

print(paste("The overall relevant percentage is: ", overall_percentage,"%"))
```

6.1.6 A fair coin is tossed twice.

Let E1 be the event that both tosses have the same outcome, that is,
E1 = (HH, TT).
Let E2 be the event that the first toss is a head, that is, E2 = (HH, HT).
Let E3 be the event that the second toss is a head, that is, E3 = (TH, HH).
Show that E1, E2, and E3 are pairwise independent but not mutually independent. 
```{r}
# sample space for two coin tosses
sample_space <- c("head-head", "head-tail", "tail-head", "tail-tail")

# events
E1 <- c("head-head", "tail-tail")  # Both tosses are the same
E2 <- c("head-head", "head-tail")  # First toss = head
E3 <- c("tail-head", "head-head")  # Second toss = head

# individual probabilities
P_E1 <- length(E1) / length(sample_space)
P_E2 <- length(E2) / length(sample_space)
P_E3 <- length(E3) / length(sample_space)

# pairwise intersection probabilities
P_E1_E2 <- length(intersect(E1, E2)) / length(sample_space)
P_E1_E3 <- length(intersect(E1, E3)) / length(sample_space)
P_E2_E3 <- length(intersect(E2, E3)) / length(sample_space)

# joint probability of all three 
P_E1_E2_E3 <- length(intersect(intersect(E1, E2), E3)) / length(sample_space)

# pairwise independence
PI <- list(
  E1_E2 = (P_E1_E2 == P_E1 * P_E2),
  E1_E3 = (P_E1_E3 == P_E1 * P_E3),
  E2_E3 = (P_E2_E3 == P_E2 * P_E3)
)

mutual_independence <- (P_E1_E2_E3 == P_E1 * P_E2 * P_E3)

print("Pairwise Independence:")
print(PI)
print("Mutual Independence:")
print(mutual_independence)
```